---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.height= 5, fig.width=5,
  fig.align = "center"
)
```

# aftQnP

<!-- badges: start -->
<!-- badges: end -->

The goal of aftQnP is to provide a statistical tool to fit a semi-parametric accelerated failure time (AFT) mixture cure model. Gaussian basis functions are used to approximate the baseline hazard function and maximum penalised likelihood estimation is used to obtain regression estimates and smooth estimates of the baseline hazard. This method allows partly interval-censored data which includes events, left, right and interval-censored observations.

## Installation

You can install the aftQnP package from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("Isabellee4555/Isabel_Li_Mres_Thesis_Rcode")
```
## Example

This is a basic example which shows you how to fit a semi-parametric AFT mixture cure mode:

```{r example}
library(aftQnP)
require(survival)
# load data
data("ptces")
# create Surv object
formula_aft <- Surv(y_L, y_R, type = "interval2") ~ X1 + X2 + X3 - 1
# fit model
model.fit <- aftsur(formula = formula_aft, cure_var = ~ Z1 + Z2 + Z3, offset = TRUE, data = ptces)

```
To plot a predicted survival curve:

```{r survival}
plot_sur(fit = model.fit, x = c(0.5, 2, -0.5))
```

To plot a predicted hazard curve:
```{r hazard}
plot_hz(fit = model.fit, x = c(0.5, 2, -0.5))
```
