---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.height= 5, fig.width=5,
  fig.align = "center"
)
```

# aftQnP

<!-- badges: start -->
<!-- badges: end -->

The goal of <code>aftQnP</code> is to provide a statistical tool for fitting a semi-parametric accelerated failure time (AFT) mixture cure model. Gaussian basis functions are employed to approximate the baseline hazard function, and maximum penalized likelihood estimation is used to obtain regression estimates and smooth estimates of the baseline hazard. This method allows for the handling of partly interval-censored data, which includes events, left-censored, right-censored, and interval-censored observations.

## Installation

You can install the <code>aftQnP</code> package from [GitHub](https://github.com/) with:

``` r
install.packages("devtools")
devtools::install_github("Isabellee4555/aftQnP")
```
## Fit a Model using a Simulated Dataset

This is a basic example which shows you how to fit a semi-parametric AFT mixture cure mode:

<code>simu_data</code> is a simulated dataset supplied by the <code>aftQnP</code> Package. This simulated data includes 500 observations with event, left, right, or interval censored survival data. The <code>survival</code> Package is required to run the proposed model. Model fitting is handled by the function <code>aftsur</code>, where the first argument <code>formula</code> is a formula for the latency (modelling the expected survival time for the non-cured group). The second argument <code>cure_var</code> is a formula for the incidence (modelling the chance of being cured). We set <code>offset = TRUE</code> as the intercept covariate <code>Z1</code> is included in the data. Alternatively, you can set <code>cure_var = ~ Z2 + Z3</code> and <code>offset = FALSE</code>. The function <code>aftsur</code> will fit the model and return an instance of the <code>aftsur</code> class.
```{r example}
library(aftQnP)
require(survival)

# load data
data("simu_data")

# create a formula using a Surv
formula_aft <- Surv(y_L, y_R, type = "interval2") ~ X1 + X2 - 1

# fit a model
aft_fit <- aftsur(formula = formula_aft, cure_var = ~ Z1 + Z2 + Z3, offset = TRUE, data = simu_data)
```

## Summary Output

We can use a generic function <code>summary()</code> to obtain a summary for the model.
```{r summary}
summary(aft_fit)
```

## Make a Prediction

We can make a prediction using the fitted model. For example, the following code predict the baseline survival probability at timepoint 0.5, 1 and 1.5. Please note that x needs to be supplied as a dataframe if not NULL.
```{r}
predict(aft_fit, x = NULL, type = "survival", time = c(0.5, 1, 1.5), interval = TRUE)
```


We can also make a prediction for a specific observation, for example:
```{r}
# create a dataframe with the same structure as the training data
test_data <- data.frame(X1 = factor("No", levels = c("No", "Yes")),
           X2 = -0.2)

# predict at timepoint 0.5
predict(aft_fit, x = test_data, type = "survival", time = c(0.5), interval = TRUE)
```

You can also input multiple observations. For example, we can take the first 5 observations from the training data and predict their hazard rates at timepoint 0.5.

```{r}
predict(aft_fit, x = simu_data[1:5, c("X1", "X2")], type = "hazard", time = c(0.5), interval = TRUE)
```


## Plot a Predicted Baseline Survival Curve

<code>aftQnP</code> also provides graphic functions: <code>plot_sur</code> and <code>plot_hz</code>. These functions plot the estimated survival and hazard functions over time for a given observation. When <code>x</code> is not supplied, the function returns the plot for baseline estimates. For example, the following code will plot the estimated baseline survival function. Please note that <code>x</code> is a dataframe that contains latency variables with the same structure as the training data. Unlike the 'x' in the <code>predict</code> function, only one row of the dataframe is allowed in <code>plot_sur</code> and <code>plot_sur</code>
```{r survival}
plot_sur(fit = aft_fit, x = NULL)
```

## Plot a Predicted Baseline Hazard Curve

Finally, we can make prediction on the hazard function using a given latency covariates. In this case, we use the <code>test_data</code> that we just generated.
```{r hazard}
plot_hz(fit = aft_fit, x = test_data)
```
